Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-24 ms.tex
Some modifications to table
Core appreciation day
lx

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ \\
\hline
$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
\hline
$    10^{ 6 }$ & 300 & 0.8 & $>$ & $ 1.3 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ & No \\
$    10^{ 6 }$ & 600 & 0.8 & $>$ & $ 2.2 \times 10^{ -6 }$ & $ 8. 10^{ 3 }$ & No \\
$    10^{ 6 }$ & 1200 & 0.8 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -4 }$ & 6.5 & No \\
$    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.8 & $>$ & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & 1.4 & Yes \\
$    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 & No \\
$    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & 4.7 & Yes \\
$    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & 1.2 & Yes \\
$    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ & 4.6 & Yes\\
$10^{8}\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & Yes & \\
$    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ & 0.43 & Yes \\
$    10^{ 6 }$ & 1200 & 0.1 & $>$ & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.1 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & 4.6 & Yes \\
\hline
\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  Thermally unstable solutions are shown in bold text.  $^{(e)}$ Is solution thermally unstable?
$\dagger$Calculated including radiative cooling, assuming $\eta =
0.04$.  {\bf  BDM: (3) make sure all combinations of vw and mbh
  are included. AG: Realized that the solution I ran earlier, with
  cooling was actually a solution that would be thermally unstable
  according to our thermal instability. I am worried that this
  solution may not be representative due to the small break radius. BDM: change TI column to simply bolding tcool ratio in those cases which are thermally unstable.}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

Figure \ref{fig:vwSources} shows that the CNM heating rate due to the average star formation history of a galaxy is predicted to be approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter, $\dot{M}/\dot{M}_{\rm edd}$ increases with SMBH
mass $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  This dependence, show more precisely in Figure XXX, appears in contradiction with the nuclear X-ray luminosities of
quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Miller+15}.

Figure~\ref{fig:miller} shows our resulting predictions for $\langle L_{X}/L_{\rm edd} \rangle =\epsilon_X \Mdot c^2$ as a function of black hole mass for core (blue) and cusp (green) galaxies.  The left
panel is calculated assuming a constant low value for the radiative efficiency $\epsilon_X =
10^{-4}$ typical of those estimated for low luminosity AGN (e.g.,
\citealt{DiMatteo+00}, \citealt{Ho:2009a}) and SgrA* (e.g.,
\citealt{Quataert+99}, \citealt{Quataert:2004a}), while the right
panel shows an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$
that depends on the Eddington ratio in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).  Superimposed with the theoretical curves
are symbols showing X-ray measurements (stars) and upper limits
(triangles) compiled by \citet{Miller+15}, along with the best power-law
fit (red line) and the X-ray detection threshold (gray line).  Finally, purple, orange, and {\bf brown} lines
orange lines show the maximum accretion rates for thermally stable
accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out
(eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]), respectively.

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
  \hline
  {$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
  \hline
  $    10^{ 6 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
  $    10^{ 6 }$ & 600 & 0.8 & 100 & $ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
  $    10^{ 6 }$ & 1200 & 0.8 & 100 & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
  $    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
  $    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
  $    10^{ 7 }$ & 1200 & 0.8 & 100 & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
  $    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
  $    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
  $    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
  $    10^{ 7 }$ & 300 & 0.8 & 25 & $ 7.8 \times 10^{ -5 }$ & 17 \\
  $    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 \\
  $    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
  $    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
  $    10^{ 8 }$ & 300 & 0.8 & 25 & $ 1.9 \times 10^{ -4 }$ & 12 \\
  $    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ &
  $\mathbf{4.6}$ \\
  $    10^{ 8 \dagger}$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ &
  $\mathbf{5.6}$ \\
  $    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ &
  $\mathbf{0.43}$ \\
  \hline
  $    10^{ 6 }$ & 1200 & 0.1 & 100 & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
  $    10^{ 7 }$ & 1200 & 0.1 & 100 & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
  $    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
  $    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
  $    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
  $    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
  $    10^{ 8 }$ & 600 & 0.1 & 100 & $ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
  $    10^{ 6 }$ & 600 & 0.1 & 25 & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
  $    10^{ 6 }$ & 600 & 0.1 & 50 & $ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
  $    10^{ 7 }$ & 600 & 0.1 & 25 & $ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
  $    10^{ 7 }$ & 600 & 0.1 & 50 & $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
  $    10^{ 8 }$ & 600 & 0.1 & 25 & $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
  $    10^{ 8 }$ & 600 & 0.1 & 50 & $ 6.0 \times 10^{ -5 }$ & 56 \\
  \hline

\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  Thermally unstable solutions are shown in bold
text.
 {\bf  BDM: (3) make sure all combinations of vw and mbh
  are included. AG: Realized that the solution I ran earlier, with
  cooling was actually a solution that would be thermally unstable
  according to our thermal instability. I am worried that this
  solution may not be representative due to the small break radius.}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g., \citealt{Ho08} and references therein).  Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  This dependence, shown directly in Figure XXX, appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Miller+15}.

Figure~\ref{fig:miller} shows our predictions for $\langle L_{X}\rangle =\epsilon_X \epsilon_{\rm bol} \Mdot c^2$ in Eddington units as a function of black hole mass for core (blue) and cusp (green) galaxies, where $\epsilon_{\rm bol} = L_{X}/L_{\rm bol}= 0.1$ is the assumed bolometric correction appropriate for low luminosity AGN (\citealt{Ho08}).  The left panel is calculated assuming a constant low value for the radiative efficiency $\epsilon_X = 10^{-4}$, typical of those estimated for low luminosity AGN (e.g.,
\citealt{DiMatteo+00}, \citealt{Ho:2009a}) and SgrA* (e.g.,
\citealt{Quataert+99}, \citealt{Quataert:2004a}).  The luminosity shown in the right
panel instead assumes an efficiency of $\epsilon_X= \dot{M}/\dot{M}_{\rm edd}$ that depends on $\dot{M}$ in the way predicted by models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}).  Superimposed with the theoretical curves
are symbols showing X-ray measurements (stars) and upper limits
(triangles) compiled by \citet{Miller+15}, along with the best power-law
fit (red line) and the X-ray detection threshold (gray line).  Finally, purple, orange, and {\bf brown} lines
orange lines show the maximum accretion rates for thermally stable
accretion (eq.~[\ref{eq:Mdotmax}]), as set by SN Ia blow-out
(eq.~[\ref{eq:eddr_Ia}]), and as allowed by Compton heating feedback (eq.~[\ref{eq:MdotC}]), respectively.
